---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(stringr)
```

# stpvers

 
Die stpvers ist eine Kopie von tidyverse  und ladet die library stpAPA2, stpOutput, stpAggregate und stpData.  
The stpvers package is designed to make it easy to install and load core packages from the stp4 in a single command.

Overview
--------

library(stpvers) 

-   `is_irgendwas` Prüft eine Bedingung.
-   `as_irgenwas` Transformiert einen Vektor zu irgendwas.
-   `test_output` Testet den Output aus stpAPA2 ob er mit stpOutput verarbeitet werden kann.
-  `CreateProjekt` Projekt Erstellung mit Kunden-Datenblatt sowie die der Folder-Strucktur mit den R-Files.
 



## Installation
### Requirements
To use `stpvers` you need to make sure the following software is installed on your computer:
  
- [R](http://www.r-project.org/) (3.4.3 or later)
- [RStudio](http://www.rstudio.com/) is optional



### Install stpvers
Once all that is taken care of, install `stpvers` from GitHub:
  
~~~{r}
devtools::install_github("stp4/stpvers")
# devtools::install_github("stp4/stp25")

devtools::install_github("stp4/stp25APA2")
devtools::install_github("stp4/stp25output")
devtools::install_github("stp4/stp25data")
devtools::install_github("stp4/stp25aggregate")
devtools::install_github("stp4/stp25plot")
 
~~~


### Usage

```{r}


library(stpvers)
getwd()

isFALSE(TRUE)

```

Please note that this project is released only as an experimental project.

